\documentclass{article}

\usepackage{enumitem}
\usepackage{url}

\title{\bfseries CS311: Project 1}
\author{Uddeep Karki}
\date{\today}

\linespread{1.24}

\begin{document}

\maketitle

\begin{itemize}
\item Repository Link:
  \url{https://github.com/uddeepk/cs311-fall21}

\item Git Commits:
  \url{https://github.com/uddeepk/cs311-fall21/commits}

  \item This homework took approximately 5 hours to complete.  
\end{itemize}

\section{Design}

This project contains the Delivery class which consists of the header, and source files. This class contains the private members the product name, the quantity to be delivered, and the calendar month in integers. It possesses a default constructor, 3-parameter constructor, getters and setters for each data member, string representation function, output stream operator, and an empty check. The header file only contains the declarations for the member functions. The source file contains all the definitions for the member functions. The Delivery class was created to be used with the Professor's delivery\_test.cpp, and the doctest framework.

\section{Post Mortem}

All the test passed. The work that was put in was not overbearing. It was a good refresher for C++ classes. \\
However, I made silly mistakes, and should have compiled as I went. I also did not use branching. For a straight forward class, it was just an hour of debugging. However, such practices would impede my work on bigger projects.

\section{Answers to Question/ Goals for future}

\begin{enumerate}
\item Compile frequently
\item Prevent errors from copying. Check logic, semicolons, and braces.
\item Practice Git branching
  
\end{enumerate}


\section{Delivery}

\subsection{Sample Output/Screenshot}

All tests pass.
TODO: Post a picture
\subsection{Git Commit Messages}

\subsection{Source Code}

TODO: Attach Source Code
\end{document}
